Discrete Quantum Theories and Computing

### 2019-03-28 dissertation.tex
dissertation.lyx "6.1 Conclusion" Updating...

Before what we can do further based on this thesis, let's summarize
what we have done previously.\todo{Keep writing\ldots}

>>>>

Before what we can do further based on this thesis, let's summarize
what we have done previously. In Chapter~\ref{chap:Conventional-Quantum-Theory},
we reviewed what was established in CQT. In particular, Sec.~\ref{CQC1qubitBloch.sec}
studied the geometrical structure of quantum states to prepare replacing
the conventional projective Hilbert space~$\CP{D-1}$ by its discrete
analog in Chapter~\ref{chap:Unrestricted-Finite-Fields} and~\ref{chap:DQT=000026DQC}.
Since the replacing state spaces are discrete, after \todo{Keep writing\ldots}
